Hypertension and microbiome

### 2019-06-07 articletwo.Rmd
Renaming

```{r maaslin runs, results = 'hide'} 
if (!file.exists("rds/maaslin.rds")) {
    pseq.genus.core <- core(pseq.genus, detection = 0.001, prevalence = 0.01)
    pseq.genus.core.viruses <- taxa(pseq.genus.core.comp) %>% mygrep(word = "virus$", complement = TRUE)
    pseq.genus.core.pruned <- prune_taxa(pseq.genus.core.viruses, pseq.genus.core.comp)

>>>>

```{r maaslin runs, results = 'hide'} 
if (!file.exists("rds/maaslin.rds")) {
    pseq.genus.core <- core(pseq.genus, detection = 0.001, prevalence = 0.01)
    pseq.genus.core.viruses.names <- taxa(pseq.genus.core) %>% mygrep(word = "virus$", complement = TRUE)
    pseq.genus.core.pruned <- prune_taxa(pseq.genus.core.viruses.names, pseq.genus.core.comp)
